Partridge: An effective system for the automatic classification of the types of academic papers

### 2013-08-10 doc/bcspaper/article.tex
Fixed reference to orange and capitalised Leverhulme

\begin{acknowledgement} We thank the Leverhulme trust for the support to Dr
Liakata's Early Career Fellowship and also EMBL-EBI, Cambridge UK for the
facilities offered to Dr Liakata.  \end{acknowledgement}

>>>>

\begin{acknowledgement} We thank the Leverhulme Trust for the support to Dr
Liakata's Early Career Fellowship and also EMBL-EBI, Cambridge UK for the
facilities offered to Dr Liakata.  \end{acknowledgement}
